Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-06-06 manuscript/manuscript.Rmd
Fixing clockplot bug depending on factor levels

both_min_model <- rbind(FT2040_features, MS3000_features) %>%
  select(feat_class, med_cor, med_SNR) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)
best_feats <- MS3000_features %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(pred_prob=predict(object=both_min_model,newdata = ., type = "response")) %>%
  mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
  select(feature, feat_class, pred_class)
clockplot_data <- norm_area_data %>%
  right_join(best_feats, by = join_by(feature)) %>%
  left_join(file_data %>% select(filename, depth), by = join_by(filename))

>>>>

both_min_model <- rbind(FT2040_features, MS3000_features) %>%
  select(feat_class, med_cor, med_SNR) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)
best_feats <- MS3000_features %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(pred_prob=predict(object=both_min_model,newdata = ., type = "response")) %>%
  mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
  select(feature, feat_class, pred_class)
clockplot_data <- norm_area_data %>%
  right_join(best_feats, by = join_by(feature)) %>%
  left_join(file_data %>% select(filename, depth), by = join_by(filename)) %>%
  mutate(depth=factor(depth, levels=c("15m", "DCM", "175m")))
